MS Prelim Data K23, using Depression T=3.09 mask

### 2022-07-20 msdepression/scripts/Descriptives_potential_paper_1_20220622.Rmd
Add files via upload

#have to pull out just the pieces I'm interested in; this is for ALL subjects
just_empi <- subset(df_demo_and_fascicles, select = c("EMPI"))
added_to_fascicles <- merge(just_empi, fascicle_proportions, by = c("EMPI"))
melted_df <- melt(added_to_fascicles, id.vars = c("EMPI", "EXAM_DATE"))

@@

>>>>

#have to pull out just the pieces I'm interested in; this is for ALL subjects
just_empi <- subset(df_demo_and_fascicles, select = c("EMPI"))
added_to_fascicles <- unique(merge(just_empi, fascicle_proportions, by = c("EMPI")))
melted_df <- melt(added_to_fascicles, id.vars = c("EMPI", "EXAM_DATE"))

@@

#####
#### look at mean fascicle volume across participants and transpose

# drop exam date and empi, and transpose
fascicles_alone_df <- t(fascicle_proportions[,!(colnames(fascicle_proportions) %in% c("EMPI", "EXAM_DATE"))])
fascicle_names <- rownames(fascicles_alone_df)

#take row means
fascicles_alone_rowMeans <- data.frame(fascicle_names, rowMeans(fascicles_alone_df))
names(fascicles_alone_rowMeans) <- c("fascicle", "value")

#sort based on overlap
fascicle_values_sorted_by_overlap <- fascicles_alone_rowMeans

fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = fascicle_values_sorted_by_overlap$fascicle[order(fascicle_values_sorted_by_overlap$value)])

######## Histograms/bar graphs
#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
hist(x=fascicle_values_dep_sorted_by_overlap$prop_in_mask, main = "Histogram Affected Streamlines", xlab = "Proportion Volume per Fascicle Affected", breaks = 20)

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
sorted_ggplot

### 2022-07-20 msdepression/scripts/K23_prelim_data_using_dep_T_3_09_mask_20220630.Rmd
Add files via upload

  A note on the "depression network." This network was made by Shan Siddiqi in Michael Fox's group by doing a conglomeration of TMS datasets, stroke datasets, Nature Human Behavior 2021 (https://www.nature.com/articles/s41562-021-01161-1). It is an unthresholded mask (which I think is in Ts per their supplement). To use it, I binarized it, and then used it as an ROI and calculated, per fascicle, the proportion of the volume occupied by the fascicle that intersected with the depression mask to the whole volume of the fascicle. Most fascicles were either entirely overlapping or entirely outside the depression mask. We consider the fascicles that had any intersection with the binary depression mask to be within the depression mask, or "indepnet." 47 out of 87 fascicles are in this network. We have an even tighter mask "indepnet_10percent", which indicates that at least 10% of a fascicle's volume intersected or overlapped with the depression mask. 15 are in this network. "in_nondep_net" refers to brain regios that completely avoided the depression network (i.e. had no shared volume of overlap). 40 are in this network.

@@

@@

@@

#have to pull out just the pieces I'm interested in
just_dep_and_empi <- subset(data_empi_acc_f_phq, select = c("EMPI", "depGroupVar"))
added_dep_to_fascicles <- merge(just_dep_and_empi, fascicle_proportions, by = c("EMPI"))
melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))

@@

#print(q)
#print(r)
print(r_color)
#print(x)
#print(y)
#print(z)
```

@@

#isolate out only the depressed group and healthy group, make a column that sums up the total prop lost)
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
   mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

@@

@@

@@

@@

@@

dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
  mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ### when I filter and remove fascicles where there was no loss at all, the depression vs healthy findings go away
#  filter(total_fascicle_prop_lost > 0) %>%
  ungroup()

@@

@@

```{r sexdep_effects_fascicles_unique}

>>>>

  A note on the "depression network." This network was made by Shan Siddiqi in Michael Fox's group by doing a conglomeration of TMS datasets, stroke datasets, Nature Human Behavior 2021 (https://www.nature.com/articles/s41562-021-01161-1). It is an unthresholded mask (which I think is in Ts per their supplement). To use it, I binarized it, thresholded clusters (3.09) and then used it as an ROI and calculated, per fascicle, the proportion of the volume occupied by the fascicle that intersected with the depression mask to the whole volume of the fascicle. Most fascicles were either entirely overlapping or entirely outside the depression mask. We consider the fascicles that had any intersection with the binary depression mask to be within the depression mask, or "indepnet." 62 out of 87 fascicles are in this network. We have an even tighter mask "indepnet_10percent", which indicates that at least 10% of a fascicle's volume intersected or overlapped with the depression mask. 21 are in this network. "in_nondep_net" refers to brain regios that completely avoided the depression network (i.e. had no shared volume of overlap). 25 are in this network.

@@

fascicle_names_dep_network_15_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$prop_in_mask >= 0.15)] #n=13

@@

a<-ggplot(data = fascicle_volumes_dep, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(a)

#sort based on overlap
fascicle_values_dep_sorted_by_overlap <- fascicle_volumes_dep
fascicle_values_dep_sorted_by_overlap$prop_in_mask[is.na(fascicle_values_dep_sorted_by_overlap$prop_in_mask)] = 0
fascicle_values_dep_sorted_by_overlap$fascicle <- factor(fascicle_values_dep_sorted_by_overlap$fascicle, levels = fascicle_values_dep_sorted_by_overlap$fascicle[order(fascicle_values_dep_sorted_by_overlap$prop_in_mask)])

plot_all_fascicles_r_and_l_sep <-ggplot(data = fascicle_values_dep_sorted_by_overlap, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(plot_all_fascicles_r_and_l_sep)

#get top quartile
quartile <- round((dim(fascicle_values_dep_sorted_by_overlap)[1] / 4),0)
dep_network_names_top_quartile<- (fascicle_values_dep_sorted_by_overlap[order(fascicle_values_dep_sorted_by_overlap$prop_in_mask, decreasing = TRUE),])$fascicle[1:quartile]

```{r mean_R_and_L_dep_network}

#this will make a data frame that contains each of the fascicles with r & l sides, and take a mean. It will then add them to a data frame with the midline structures and make a histogram of them

#some preprocessing because there is one section of the data frame (C_PH_L, C_PHP_L, C_PHP_R and C_PH_R) where the L , L, R, R is out of sync with the rest. 
fascicle_dep_data_frame_rows_switched <- fascicle_volumes_dep

#make nas into 0
fascicle_dep_data_frame_rows_switched$prop_in_mask[is.na(fascicle_dep_data_frame_rows_switched$prop_in_mask)] = 0

#reorder by moving C_PH_R up before C_PHP_L, and shifting the others down

c_ph_r_row <- fascicle_dep_data_frame_rows_switched[10,]
c_php_rows <- fascicle_dep_data_frame_rows_switched[8:9,]

fascicle_dep_data_frame_rows_switched[8,] <- c_ph_r_row
fascicle_dep_data_frame_rows_switched[9:10,] <- c_php_rows

#get names of fascicles w/r and l
fascicle_names_w_r_and_l_split <- fascicle_dep_data_frame_rows_switched$fascicle[(grep("_", fascicle_dep_data_frame_rows_switched$fascicle))]

#get names of fascicles that are midline
fascicle_names_midline <- fascicle_dep_data_frame_rows_switched$fascicle[grep("_", fascicle_dep_data_frame_rows_switched$fascicle, invert=TRUE)]

#separate out right and left, important because for some reason they hae a different order
fascicle_names_r <- fascicle_names_w_r_and_l_split[(grep("_R$", fascicle_names_w_r_and_l_split))]
fascicle_names_l <- fascicle_names_w_r_and_l_split[(grep("_L$", fascicle_names_w_r_and_l_split))]

#get the fascicle names of lateral structures, we will use the right side as default
fascicle_names_of_lateral_structs <- gsub("_R$", "", fascicle_names_r)

#get values of right and left side structs
fascicle_values_r <- fascicle_dep_data_frame_rows_switched$prop_in_mask[grep("_R$", fascicle_names_w_r_and_l_split)]
fascicle_values_l <- fascicle_dep_data_frame_rows_switched$prop_in_mask[grep("_L$", fascicle_names_w_r_and_l_split)]

#take mean of r and l side and put in new df
df_r_and_l_mean <-  (fascicle_values_r + fascicle_values_l)/2
df_r_and_l <- data.frame(fascicle_names_of_lateral_structs, df_r_and_l_mean)
names(df_r_and_l) <- c("fascicle", "prop_in_mask")

#pull out midline names and values
fascicle_values_midline <- fascicle_dep_data_frame_rows_switched$prop_in_mask[grep("_", fascicle_dep_data_frame_rows_switched$fascicle, invert=TRUE)]
df_midline<- data.frame(fascicle_names_midline, fascicle_values_midline)
names(df_midline) <- c("fascicle", "prop_in_mask")

#combine data frames
fascicle_values_dep_not_lateralized <- data.frame(rbind(df_r_and_l, df_midline))

#sort based on overlap
fascicle_values_dep_sorted_by_overlap <- fascicle_values_dep_not_lateralized
fascicle_values_dep_sorted_by_overlap$fascicle <- factor(fascicle_values_dep_sorted_by_overlap$fascicle, levels = fascicle_values_dep_sorted_by_overlap$fascicle[order(fascicle_values_dep_sorted_by_overlap$prop_in_mask)])

#fascicle_values_dep_sorted_by_overlap <- fascicle_values_dep_not_lateralized[order(fascicle_values_dep_not_lateralized$prop_in_mask),]

######## Histograms for depression network
#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
hist(x=fascicle_values_dep_sorted_by_overlap$prop_in_mask, main = "Histogram Affected Streamlines in Dep Net, not lateralized", xlab = "Proportion Volume per Fascicle Affected", breaks = 20)

sorted_ggplot<-ggplot(data = fascicle_values_dep_sorted_by_overlap, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot)

##new depression network, top quartile of the 46 -> top 12. This step makes a new df after ordering the previous data frame in reverse order, highest numbers at top, and then takes the top quartile)
quartile <- round((dim(fascicle_values_dep_sorted_by_overlap)[1] / 4),0)
dep_network_names_top_quartile_r_and_l_meaned<- (fascicle_values_dep_sorted_by_overlap[order(fascicle_values_dep_sorted_by_overlap$prop_in_mask, decreasing = TRUE),])$fascicle[1:quartile]

@@

#have to pull out just the pieces I'm interested in
just_dep_and_empi <- subset(data_empi_acc_f_phq, select = c("EMPI", "depGroupVar"))
added_dep_to_fascicles <- unique(merge(just_dep_and_empi, fascicle_proportions, by = c("EMPI")))

melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))

@@

#print(q)
#print(r)
print(r_color)
#print(x)
#print(y)
#print(z)

###########################################################################################################
##### Looking at distribution of disease across fascicles across group and within healthy and depressed ###
###########################################################################################################

#### look at mean fascicle volume across participants and transpose
# drop exam date and empi, and transpose
fascicles_alone_df <- t(added_dep_to_fascicles[,!(colnames(added_dep_to_fascicles) %in% c("EMPI", "EXAM_DATE", "depGroupVar"))])
fascicle_names <- rownames(fascicles_alone_df)

#take row means
fascicles_alone_rowMeans <- data.frame(fascicle_names, rowMeans(fascicles_alone_df))
names(fascicles_alone_rowMeans) <- c("fascicle", "value")

#sort based on overlap
fascicle_values_sorted_by_overlap <- fascicles_alone_rowMeans

#make this separate in case I want to use this distribution for ranking depressed and healthy networks. 
order_of_mean_values_overall <- fascicle_values_sorted_by_overlap$fascicle[order(fascicle_values_sorted_by_overlap$value)]

fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = fascicle_values_sorted_by_overlap$fascicle[order(fascicle_values_sorted_by_overlap$value)])

######## Histograms/bargraphs
#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
hist(x=fascicle_values_dep_sorted_by_overlap$prop_in_mask, main = "Histogram Affected Streamlines", xlab = "Proportion Volume per Fascicle Affected", breaks = 20)

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot)

######### 
#############
#### look at mean fascicle volume across healthy participants and transpose
#############

# drop exam date and empi, and transpose
healthy_group_fascicles <- added_dep_to_fascicles[(added_dep_to_fascicles$depGroupVar == 1),]
fascicles_alone_df <- t(healthy_group_fascicles[,!(colnames(healthy_group_fascicles) %in% c("EMPI", "EXAM_DATE", "depGroupVar"))])
fascicle_names <- rownames(fascicles_alone_df)

#take row means
fascicles_alone_rowMeans <- data.frame(fascicle_names, rowMeans(fascicles_alone_df))
names(fascicles_alone_rowMeans) <- c("fascicle", "value")

#sort based on overlap
fascicle_values_sorted_by_overlap <- fascicles_alone_rowMeans

fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = fascicle_values_sorted_by_overlap$fascicle[order(fascicle_values_sorted_by_overlap$value)])

######## Histograms/bargraphs
#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
hist(x=fascicle_values_dep_sorted_by_overlap$prop_in_mask, main = "Histogram Affected Streamlines in Non Depressed", xlab = "Proportion Volume per Fascicle Affected", breaks = 20)

sorted_ggplot_healthy<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected in Non Depressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_healthy)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_healthy_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected Ordered by mean values NonDepressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_healthy_ordered)

###########
#### look at mean fascicle volume across depressed participants and transpose
###########
# drop exam date and empi, and transpose
depressed_group_fascicles <- added_dep_to_fascicles[(added_dep_to_fascicles$depGroupVar == 2),]
fascicles_alone_df <- t(depressed_group_fascicles[,!(colnames(depressed_group_fascicles) %in% c("EMPI", "EXAM_DATE", "depGroupVar"))])
fascicle_names <- rownames(fascicles_alone_df)

#take row means
fascicles_alone_rowMeans <- data.frame(fascicle_names, rowMeans(fascicles_alone_df))
names(fascicles_alone_rowMeans) <- c("fascicle", "value")

#sort based on overlap
fascicle_values_sorted_by_overlap <- fascicles_alone_rowMeans

fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = fascicle_values_sorted_by_overlap$fascicle[order(fascicle_values_sorted_by_overlap$value)])

######## Histograms/bargraphs
#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
hist(x=fascicle_values_dep_sorted_by_overlap$prop_in_mask, main = "Histogram Affected Streamlines", xlab = "Proportion Volume per Fascicle Affected Depressed", breaks = 20)

sorted_ggplot_depressed<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected Depressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_depressed)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_depressed_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected Ordered by mean values Depressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_depressed_ordered)
```

@@

#isolate out only the depressed group and healthy group, make a column that sums up the total prop lost)
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
  mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  mutate(total_fascicle_prop_lost_indepnet_15_percent =
           rowMeans(across(fascicle_names_dep_network_15_percent))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

@@

#look at within depression network in fascicles where at least 15% of the volume of the fascicle was in dep network
#yes, p=0.054, mean dep = 30%, mean nondep = 25%
total_volume_lost_dep_vs_healthy_unique_in_dep_network_15percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_15_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_15_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F)

@@

# Grouped
barplot <- ggplot(data, aes(x=Diagnosis,fill=Diagnosis, y=value)) + 
  geom_bar(stat="identity", position=position_dodge(0.9)) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  ylim(0,40) +
  theme(axis.text = element_text(size = 12, colour = "black"))

@@

# Grouped
barplot <- ggplot(data, aes(x=reorder(Diagnosis, -value),fill=Diagnosis, y=value)) + 
  geom_bar(stat="identity", colour="black", width=0.8, size=1.5) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) +
  scale_fill_manual(values = c("#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=20),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) #comment out if you want colored graph

@@

#fdr corrected only dep 15% mask
fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_volumes_dep_network$prop_in_mask >= 0.15)]
fascicle_anova_fdr<- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

@@

nondep15_net <- fascicle_names[!(fascicle_names %in% fascicle_names_dep_network_15_percent)]

dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
  mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  mutate(total_fascicle_prop_lost_dep_network_15_percent = 
           rowMeans(across(fascicle_names_dep_network_15_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network_15_percent = 
           rowMeans(across(nondep15_net))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ### when I filter and remove fascicles where there was no loss at all, the depression vs healthy findings go away
#  filter(total_fascicle_prop_lost > 0) %>%
  ungroup()

@@

volume_lost_dep15_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_dep_network_15_percent,
dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network, var.equal = F) #mean dep net = 28%, mean non_dep_net = 14%, p 2.2 * 10^-16

volume_lost_dep15_vs_nondep_network_15_percent_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_dep_network_15_percent,
dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network_15_percent, var.equal = F) #mean dep 15 net = 28%, mean all fascicles not in 15% net = 26%, p=0.13

@@

```{r sexdep_effects_fascicles_unique_age_cov}
